prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-06-14 inst/MyArticle/PosterBioconductor.Rmd
New hexsticker

---
title: |
  <center>The __prolfqua__ R-package</center> 
  <center>for Analysing Proteomics Label Free Quantification Experiments <center>
author: 
  - name: Witold Wolski
    affil: 1; 2
    orcid: '0000-0002-6468-120X'
  - name: Paolo Nanni
    affil: 1
    orcid: '0000-0001-8429-3557'
  - name: Jonas Grossmann
    affil: 1; 2
    orcid: '0000-0002-6899-9020'
  - name: Maria D'Errico
    affil: 1; 2
    orcid: '0000-0001-9467-9058'
  - name: Ralph Schlapbach
    affil: 1
    orcid: '0000-0002-7488-4262'
  - name: Christian Panse
    affil: 1; 2
    orcid: '0000-0003-1975-3064'

affiliation:
  - num: 1
    address: Functional Genomics Center Zurich - ETH Zurich/University of Zurich (https://www.fgcz.ch/)
  - num: 2
    address: Swiss Institute of Bioinformatics (https://www.sib.swiss/)
column_numbers: 5
poster_height: "38in"
poster_width: "65in"
title_textsize:	"100pt"
font_family: Monaco
primary_colour: "#6f9e73"
secondary_colour: "#7d5f60"
accent_colour: "#248ce0"
titletext_fontfamily: Arial
body_textsize: "44px"
logoleft_name: ../Figures/hexStickerProlfqua.png
logoright_name: FGCZLogo.png
output: 
  posterdown::posterdown_html
bibliography: bibliography.bib

---

@@

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 7, fig.height = 5)

@@

```{r LFQData, echo=FALSE, fig.cap="Class Diagram for LFQData and related objects. The LFQData_Plotter class uses the LFQData class to implement methods for plotting.", out.width = '90%'}
knitr::include_graphics("LFQData.png")
```

@@

```{r exampleContrasts, fig.cap="(ref:exampleContrasts)", echo=TRUE, out.width = '90%'}
contrasts <- c(
  "dilution_(9/7.5)_1.2" =   "dilution.e - dilution.d",
  "dilution_(7.5/6)_1.25" =   "dilution.d - dilution.c",
  "dilution_(6/4.5)_1.3(3)" =   "dilution.c - dilution.b",
  "dilution_(4.5/3)_1.5" =   "dilution.b - dilution.a"
)
# fit model
lmmodel <- paste(lfqp$intensity_column()," ~ dilution.")
modelFunction <- strategy_lm( lmmodel, model_name = "lm")
models <- build_model(lfqp, modelFunction)
p1 <-  models$anova_histogram()
# compute contrasts from linear model and with imputation
contr <- Contrasts$new(models, contrasts) |> 
  ContrastsModerated$new()
conI <- ContrastsSimpleImpute$new( lfqp, contrasts) |> 
  ContrastsModerated$new()
tmp <- addContrastResults(contr, conI)
# visualize results
pl <- tmp$merged$get_Plotter()
p1 <- pl$histogram()$p.value
p2 <- pl$volcano()$FDR +
   theme(legend.position = "bottom")
gridExtra::grid.arrange(p1, p2, ncol = 2)

>>>>

---
title: |
  <center>The __prolfqua__ R-package</center> 
  <center>for Analysing Proteomics Label Free Quantification Experiments <center>
author: 
  - name: Witold Wolski
    affil: 1; 2
    orcid: '0000-0002-6468-120X'
  - name: Paolo Nanni
    affil: 1
    orcid: '0000-0001-8429-3557'
  - name: Jonas Grossmann
    affil: 1; 2
    orcid: '0000-0002-6899-9020'
  - name: Maria D'Errico
    affil: 1; 2
    orcid: '0000-0001-9467-9058'
  - name: Ralph Schlapbach
    affil: 1
    orcid: '0000-0002-7488-4262'
  - name: Christian Panse
    affil: 1; 2
    orcid: '0000-0003-1975-3064'
affiliation:
  - num: 1
    address: Functional Genomics Center Zurich - ETH Zurich/University of Zurich (https://www.fgcz.ch/)
  - num: 2
    address: Swiss Institute of Bioinformatics (https://www.sib.swiss/)
column_numbers: 5
poster_height: "38in"
poster_width: "65in"
title_textsize:	"100pt"
font_family: Monaco
primary_colour: "#6f9e73"
secondary_colour: "#7d5f60"
accent_colour: "#248ce0"
titletext_fontfamily: Arial
body_textsize: "44px"
logoleft_name: hexStickerProlfqua.png
logoright_name: FGCZLogo.png
output: 
  posterdown::posterdown_html
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---

@@

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 7, fig.height = 5)
library(ggplot2)
library(prolfqua)
library(tidyverse)

@@

```{r LFQData, echo=FALSE, fig.cap="Class Diagram for LFQData and related objects. The LFQData_Plotter class uses the LFQData class to implement methods for plotting.", out.width = '90%'}
knitr::include_graphics("LFQData_UML_V2.png")
```

@@

```{r exampleContrasts, fig.cap="(ref:exampleContrasts)", echo=TRUE, out.width = '90%'}
contrasts <- c(
  "dilution_(9/7.5)_1.2" =   "dilution.e - dilution.d",
  "dilution_(7.5/6)_1.25" =   "dilution.d - dilution.c",
  "dilution_(6/4.5)_1.3(3)" =   "dilution.c - dilution.b",
  "dilution_(4.5/3)_1.5" =   "dilution.b - dilution.a"
)
# fit model
lmmodel <- paste(lfqp$intensity_column()," ~ dilution.")
modelFunction <- strategy_lm( lmmodel, model_name = "lm")
models <- build_model(lfqp, modelFunction)
p1 <-  models$anova_histogram()
# compute contrasts from linear model and with imputation
contr <- prolfqua::Contrasts$new(models, contrasts) |> 
  prolfqua::ContrastsModerated$new()
conI <- prolfqua::ContrastsSimpleImpute$new( lfqp, contrasts) |> 
  prolfqua::ContrastsModerated$new()
tmp <- prolfqua::addContrastResults(contr, conI)
# visualize results
pl <- tmp$merged$get_Plotter()
p1 <- pl$histogram()$p.value
p2 <- pl$volcano()$FDR +
   theme(legend.position = "bottom")
gridExtra::grid.arrange(p1, p2, ncol = 2)

### 2022-06-14 inst/MyArticle/paper.Rmd
New hexsticker

```{r setup, include=FALSE}
## See ACS guidelines [https://publish.acs.org/publish/author_guidelines?coden=ancham#manuscript_text_components]
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 7,
                      fig.height = 5)

@@

getpath <- function(filN){
    f1 <- system.file("Benchresults",filN, package = "prolfquabenchmark")
    if(f1 == ""){
        f1 <- paste0("../../inst/Benchresults/",filN)
    }
    return(f1)
}
allBenchmarks <- readRDS(getpath("allBenchmarks.RDS"))
benchmark_msstats <- readRDS(getpath("benchmark_msstats.RDS"))
benchmark_prodA <- readRDS(getpath("benchmark_medpolish_proDA.RDS"))
msFragger <- readRDS(getpath("MSFragger_medpol_benchmark.RDS"))

@@

gridExtra::grid.arrange(p1_pAUC, pB, pC, layout_matrix=hlay)
```

@@

file.path(system.file(package = "prolfqua"), 
          "Figures/hexStickerProlfqua.png") |>
  knitr::include_graphics()
```

>>>>

```{r setup, include=FALSE}
## See ACS guidelines [https://publish.acs.org/publish/author_guidelines?coden=ancham#manuscript_text_components]
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 7,
                      fig.height = 5)
ggplot2::theme_set(ggplot2::theme_classic())

@@

getpath <- function(filN){
    f1 <- paste0("../../inst/Benchresults/",filN)
    if(f1 == ""){
        f1 <- system.file("Benchresults",filN, package = "prolfquabenchmark")
    }
    message(f1)
    return(f1)
}
allBenchmarks <- readRDS(getpath("allBenchmarks.RDS"))
benchmark_msstats <- readRDS(getpath("benchmark_msstats.RDS"))
benchmark_prodA <- readRDS(getpath("benchmark_medpolish_proDA.RDS"))
msFragger <- readRDS(getpath("MSFragger_medpol_benchmark.RDS"))

@@

gridExtra::grid.arrange(p1_pAUC, pB, pC, layout_matrix=hlay)

@@

file.path("hexStickerProlfqua.png") |>
  knitr::include_graphics()
```
